Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-05-31 R0V0.tex
Add a figure explaining the difference between the plant and the communication network graph
Add figure with simulations

\mypara Let $N>0$ be an integer and consider the graph $\mathscr{G}_p$ defined by the set of vertices $\mathscr{V}_p=\mathbb{N}_{[1,N]}$ and a set of edges $\mathscr{E}_p\subset\mathbb{N}_{[1,N]}\times\mathbb{N}_{[1,N]}$. For each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
\begin{equation}\label{eq:subsystem}
	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
\end{equation}
where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}. Given a graph $\mathscr{G}_c=(\mathbb{N}_{[1,N]},\mathscr{E}_c)$ that specifies a communication network. One of the objectives of this work is to design a feedback law $k_i^\ast=k_i(t,x_i,\vec{x}_i,X_i^\ast,\vec{X}_i^\ast,u_i^\ast)$ for \eqref{eq:subsystem} under the constraints defined by $\mathscr{G}_c$, where $\vec{x}_i\in\mathbb{R}^{\vec{n}_i}$ stands for the vector composed of states $x_j\in\mathbb{R}^{n_j}$, that are adjacent to system $i$, according to the set of edges $\mathscr{E}_c$.

@@

\mypara Figure~\ref{fig:3dsim} shows the $x$-component of a simulation of network~\eqref{eq:example} composed of three systems with the network structure as represented by the graph in Figure~\ref{fig:graph} and with input $u\equiv0$. Note that, when random initial random initial conditions are considered, the system may diverge from the neighborhood of the origin.

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\linewidth]{./imgs/3dsim.eps}
	\caption{Simulation of network~\eqref{eq:example} for 1s with input $u\equiv0$, $N=3$ and starting from random initial conditions.}
	\label{fig:3dsim}
\end{figure}

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}
	\caption{Time taken to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration. The number of agents started with one system and doubled  until the maximum that the computer could process (4 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case). Axes are on log scale.}
	\label{fig:time graph}
\end{figure}

>>>>

\mypara Let $N>0$ be an integer and consider the graph $\mathscr{G}_p$ defined by the set of vertices $\mathscr{V}_p=\mathbb{N}_{[1,N]}$ and a set of edges $\mathscr{E}_p\subset\mathbb{N}_{[1,N]}\times\mathbb{N}_{[1,N]}$. For each index $i\in\mathbb{N}_{[1,N]}$, system~\eqref{eq:general system} can be decomposed into smaller components as follows.
\begin{equation}\label{eq:subsystem}
	\dot{x}_i=f_i(x_i,\breve{x}_i)+b_i(x_i)u_i\;,
\end{equation}
where $\breve{x}_i\in\mathbb{R}^{\breve{n}_i}$ stands for the vector composed of states $x_j$ of systems that are adjacent to system~\eqref{eq:subsystem}. Given a graph $\mathscr{G}_c=(\mathbb{N}_{[1,N]},\mathscr{E}_c)$ that specifies a communication network. One of the objectives of this work is to design a feedback law $k_i^\ast=k_i(t,x_i,\vec{x}_i,X_i^\ast,\vec{X}_i^\ast,u_i^\ast)$ for \eqref{eq:subsystem} under the constraints defined by $\mathscr{G}_c$, where $\vec{x}_i\in\mathbb{R}^{\vec{n}_i}$ stands for the vector composed of states $x_j\in\mathbb{R}^{n_j}$, that are adjacent to system $i$, according to the set of edges $\mathscr{E}_c$. The difference between both graphs is illustrated in Figure~\ref{fig:graph different illustration}.

\begin{figure}[htbp!]
	\centering
%	\includegraphics[]{}
	\resizebox{.4\columnwidth}{!}{\input{./imgs/Graphs.pdf_tex}}
	\caption{Illustration of the graphs $\mathscr{G}_p$ and $\mathscr{G}_c$. The solid lines represent the edges defining $\mathscr{G}_p$ while the dashed lines represent edges defining $\mathscr{G}_c$.}
	\label{fig:graph different illustration}
\end{figure}

@@

\mypara Figure~\ref{fig:3dsim} shows simulations of the network~\eqref{eq:example} composed of four systems with the network structure as represented by the graph in Figure~\ref{fig:graph} under different inputs, and the Riemannian metric $V$. Note that, when random initial random initial conditions are considered, the system may diverge from the neighborhood of the origin.

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\linewidth]{./imgs/simulation.eps}
	\vspace{-2em}
	\caption{Simulation of network~\eqref{eq:example} with the target trajectory being the origin and under the controller obtained according to different constrains for the computation of $Y$: diagonal, neighbour and unconstrained. In contrast to these, the open loop simulation (performed with $u\equiv0$) does not converge to the origin. The bottom graph shows the variation of the Riemannian metric along the solutions of each case.}
	\label{fig:3dsim}
\end{figure}

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}\vspace{-2em}
	\caption{Time taken to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration. The number of agents started with one system and doubled  until the maximum that the computer could process (4 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case). Axes are on log scale.}
	\label{fig:time graph}
\end{figure}
